Deeply Virtual Compton Scattering measurement off bound protons

### 2018-10-01 eg6-letters/incoherent/incoherent_prl.tex
Minor updates on incoherent
Implement the English typos from the second round comments from the adhoc review

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurement of incoherent deeply 
   virtual Compton scattering (DVCS) off $^4$He. The data were accumulated 
   using a 6 GeV longitudinally polarized electron beam incident on a 
   pressurized $^4$He gaseous target placed in front of the CLAS spectrometer 
   in Hall-B at the Thomas Jefferson National Accelerator Facility. The 
   azimuthal angular ($\phi$) dependence of the BSA is studied in a wide range 
   of virtual photon and scattered proton kinematics. The Q$^2$, $x_B$, and $t$ 
   dependencies of the BSA on the bound proton are compared with the one on the 
   free proton. In the whole kinematical region of our measurements, the BSA on 
   the bound proton is smaller by $20\%$ to $40\%$, indicating possible medium 
   modification of its partonic structure. This measurement opens a new avenue 
   for studying structure of the bound nucleon and explore the origin of the 
   EMC effect using the framework of the generalized parton distributions.

@@

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
diagram for this process. In the Bjorken regime, i.e, large virtual photon 
four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
momentum transfer ($t=(p-p^\prime)^2$), the DVCS scattering process can be 
factorized, leaving the non-perturbative structure of the nucleon to be 
parametrized in terms of four chirally-even GPDs: $H$, $E$, $\widetilde{H}$, 
and $\widetilde{E}$, representing the four helicity-spin combinations of the 
quark-nucleon states \cite{Freund_Collins,Ji_Osborne}. Experimentally, we 
measure the squared sum of the Bethe-Heitler (BH) and the DVCS amplitudes. The 
BH process, where the real photon is emitted by the incident or the scattered 
electron rather than the nucleon, dominates the cross section at our 
kinematics. The BSA arises from the interference of these two terms and is 
directly sensitive to the DVCS amplitude that contains the information on the 
GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 
target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region. 
The $t$, transferred momentum squared to the recoil proton assuming an on-shell 
proton at rest, was required to be greater than a minimum allowed value at 
given Q$^2$ and W ($t>~t_{min}(=~- Q^{2}~\frac{2(1- x_{B})(1~-~\sqrt{1 
+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). Then, the exclusivity of the incoherent DVCS events was ensured 
by imposing constraints on the kinematical variables resulting from conserving 
the four-momentum in the reaction $ep\rightarrow e'p'\gamma$.  These 
kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the assymetries 
appear to be stable as a function of cut width and we see no sizeable effect 
that can be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of 
two photons. At the end of this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$ (integarted over full $x_{B}$ and $t$ ranges), 
$x_{B}$ (integarted over full $Q^{2}$ and $t$ ranges), and $t$ (integarted over 
full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of the form 
$\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$.  The main contributions to 
systematic uncertainties on these fits are from the choice of the DVCS 
exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
uncertainties sum up to less than 10\% for all data points and thus always 
remain significantly smaller than the statistical errors.

@@

FIG.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
$\phi$~=~90$^{\circ}$ ($a_{0}$ parameter from the individual fits in 
FIG.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
Within the given uncertainties, $A_{LU}$ does not indicate a strong dependence 
on $Q^2$.  The $x_{B}$ and $t$ dependencies are compared to theoretical 
calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
model uses a nuclear spectral function and considers mainly off-shell effects.  
The calculations are carried out at slightly different kinematics than our data 
but still provide important guidance. The experimental results appear to have 
smaller asymmetries especially at low $x_{B}$ than the calculations. These 
differences may arise from nuclear effects which are not taken into account in 
the model, such as long-range interactions.  On the graph for $-t$ dependence, 
we show previous measurements by the HERMES collaboration 
\cite{Airapetian:2009cga}, in which only electrons
and photons were measured. Due to the large experimental uncertainties of the HERMES 
points, the two measurements are completely compatible.

\begin{figure}[tb]
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
   represent the statistical uncertainties, while the gray bands represent the 
   systematic uncertainties. On the middle plot: the curves are theoretical 
   calculations from \cite{simonetta_2}. On the bottom: the solid (empty) green 
   circles are the HERMES $-A_{LU}$ (positron beam was used) inclusive 
measurements for the incoherent (coherent) enriched region 
\cite{Airapetian:2009cga}, the curves represent theoretical calculations from 
\cite{simonetta_2}.  } \label{fig:alu90}
\end{figure}

@@

%conclusion
In summary, we have presented the first BSA measurment associated with bound 
proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
Jefferson Lab. Our results were compared to model calculations based on 
different assumptions of the nuclear medium effects at the partonic level. The 
bound-proton BSA is largely suppressed compared to the free proton BSA. This 
surprising result opens a new avenue for progress in the understanding quarks 
and gluons in the nuclear medium.

@@

\bibitem{Dupre:2016mai} R.~Dupre, M.~Guidal and M.~Vanderhaeghen,
 %``Tomographic image of the proton,''
 Phys.\ Rev.\ D {\bf 95}, no. 1, 011501 (2017)

>>>>

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurement of incoherent deeply 
   virtual Compton scattering (DVCS) off $^4$He. The data were accumulated 
   using a 6 GeV longitudinally polarized electron beam incident on a 
   pressurized $^4$He gaseous target placed in front of the CLAS spectrometer 
   in Hall-B at the Thomas Jefferson National Accelerator Facility. The 
   azimuthal angular ($\phi$) dependence of the BSA is studied in a wide range 
   of virtual photon and scattered proton kinematics. The Q$^2$, $x_B$, and $t$ 
   dependencies of the BSA on the bound proton are compared with those on the 
   free proton. In the whole kinematical region of our measurements, the BSA on 
   the bound proton is smaller by $20\%$ to $40\%$, indicating possible medium 
   modification of its partonic structure. This measurement opens a new avenue 
   for studying structure of the bound nucleon and explore the origin of the 
   EMC effect using the framework of the generalized parton distributions.

@@

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
diagram for the DVCS process. In the Bjorken regime, i.e, large virtual photon 
four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
momentum transfer ($t=(p-p^\prime)^2$), the DVCS scattering process can be 
factorized, leaving the non-perturbative structure of the nucleon to be 
parametrized in terms of four chirally-even GPDs: $H$, $E$, $\widetilde{H}$, 
and $\widetilde{E}$, representing the four helicity-spin combinations of the 
quark-nucleon states \cite{Freund_Collins,Ji_Osborne}. Experimentally, we 
measure the squared sum of the Bethe-Heitler (BH) and the DVCS amplitudes. The 
BH process, where the real photon is emitted by the incident or the scattered 
electron rather than the nucleon, dominates the cross section at our 
kinematics. The BSA arises from the interference of these two terms and is 
directly sensitive to the DVCS amplitude that contains the information on the 
GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 
target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=\sqrt{(q+p)^2}$) greater than 2 GeV to avoid the nucleon resonance 
region.  The $t$, transferred momentum squared to the recoil proton assuming an 
on-shell proton at rest, was required to be greater than a minimum allowed 
value at given Q$^2$ and W ($t>~t_{min}(=~- Q^{2}~\frac{2(1- x_{B})(1~-~\sqrt{1 
+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). Then, the exclusivity of the incoherent DVCS events was ensured 
by imposing constraints on the kinematical variables resulting from conserving 
the four-momentum in the reaction $ep\rightarrow e'p'\gamma$.  These 
kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the assymetries 
appear to be stable as a function of cut width and we see no sizeable effect 
that can be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of 
two photons. At the end of this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$ (integrated over full $x_{B}$ and $t$ ranges), 
$x_{B}$ (integrated over full $Q^{2}$ and $t$ ranges), and $t$ (integrated over 
full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of the form 
$\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$.  The main contributions to 
systematic uncertainties on these fits are from the choice of the DVCS 
exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
uncertainties sum up to less than 10\% for all data points and thus always 
remain significantly smaller than the statistical errors.

@@

FIG.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
$\phi$~=~90$^{\circ}$ ($a_{0}$ parameter from the individual fits in 
FIG.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
Within the given uncertainties, $A_{LU}$ does not indicate a strong dependence 
on $Q^2$.  The $x_{B}$ and $t$ dependency are compared to theoretical 
calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
model uses a nuclear spectral function and considers mainly off-shell effects.  
The calculations are carried out at slightly different kinematics than our data 
but still provide important guidance. The experimental results appear to have 
smaller asymmetries especially at low $x_{B}$ than the calculations. These 
differences may arise from nuclear effects which are not taken into account in 
the model, such as long-range interactions and final state interactions of the 
knock-out proton. On the graph for $-t$ dependence, we show previous 
measurements by the HERMES collaboration \cite{Airapetian:2009cga}, in which 
only electrons and photons were measured. Due to the large experimental 
uncertainties of the HERMES points, the two measurements are completely 
compatible.

\begin{figure}[tb]
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
   represent the statistical uncertainties, while the gray bands represent the 
   systematic uncertainties. On the middle plot: the curves are theoretical 
   calculations from \cite{simonetta_2}. On the bottom plot: the solid (empty) 
   green circles are the HERMES $-A_{LU}$ (a positron beam was used) inclusive 
   measurements for the incoherent (coherent) enriched region 
   \cite{Airapetian:2009cga}, the curves represent theoretical calculations 
   from \cite{simonetta_2}.  } \label{fig:alu90}
\end{figure}

@@

%conclusion
In summary, we have presented the first BSA measurment associated with bound 
proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
Jefferson Lab. Our results were compared to model calculations based on 
different assumptions of the nuclear medium effects at the partonic level. The 
bound-proton BSA is largely suppressed compared to the free proton BSA. This 
surprising result opens a new avenue for progress in understanding the 
properties of quarks and gluons in the nuclear medium.

@@

\bibitem{Dupre:2016mai} R.~Dupr\'{e}, M.~Guidal and M.~Vanderhaeghen,
 %``Tomographic image of the proton,''
 Phys.\ Rev.\ D {\bf 95}, no. 1, 011501 (2017)
